Processing of visual and non-visual naturalistic spatial information in the "parahippocampal place area"

### 2021-02-16 paper/main.tex
Cut abstract to size (168 of 170 words)

\begin{abstract}
% < 170 words new analysis of existing data of interest to a broad section of
% our audience highlighting innovative examples of data reuse may be used to
% present compelling new findings & conclusions derived from published.
Neuroimaging studies have parcellated the human brain into distinct functional
areas.
% PPA
A region in the human hippocampal cortex termed ``parahippocampal place area''
is classically considered to be a higher visual area as increased hemodynamic
activity in the PPA correlates with the perception of static pictures of
landscapes compared to pictures of faces or objects.
% AV, AD: operationalization
In this study, we explore different ways to operationalize the perception of
spatial information in 14 subjects that were watching an audio-visual Hollywood
movie and listened to the movie's audio-description (studyforrest.org).
% auditory localizer?
Focussing on the audio-description, we test if an auditory narrative could
localize a ``visual area'' in individual subjects.
% GLM
For each naturalistic stimulus, we model hemodynamic activity via several
general linear model (GLM) $t$-contrasts that are based on annotations of
selected stimulus features.
% VIS
Current results are compared to results of classic visual localizer experiment
that we conducted previously to localize the PPA in the same participants.
% no refs in abstract (probably)
%\citep{sengupata2016extension}.  results: group AV
On a group level, results for a visual movie stimulus show significantly
increased hemodynamic activity spatially overlapping with a traditionally
localized PPA but also extending into earlier visual cortices.
% results: group AD
Results for the audio-description stimulus reveal significant activation
restricted to the anterior part of the PPA.
% results: individual AD
On an individual level, results of the audio-description show significant
bilateral clusters in the anterior PPA of nine subjects and significant
unilateral clusters in two subjects.
% conclusion: generalizability
Results suggest that increased activation in the PPA during the perception of
static pictures generalizes to the perception of spatial information embedded in
an audio-visual movie and an exclusively auditory stimulus.
% conclusion: PPA has subregions
Our results provide further evidence that the PPA can be divided into functional
subregions.
\end{abstract}

>>>>

\begin{abstract}
% < 170 words new analysis of existing data of interest to a broad section of
% our audience highlighting innovative examples of data reuse may be used to
% present compelling new findings & conclusions derived from published.
% PPA
The ``parahippocampal place area'' (PPA)
is a visual area in the human ventral stream with increased hemodynamic
activity correlated with the perception of landscape photos compared to faces or objects.
% AV, AD: operationalization
Here we investigate the perception of
spatial information in 14 individuals from the open-data resource \textit{studyforrest.org}
that were watching a two-hour Hollywood
movie and listened to the movie's audio-description.
% auditory localizer?
%in order to explore if a naturalistic auditory narrative could be used
%to localize a ``visual area''.
% GLM
We model hemodynamic activity based on annotations of selected stimulus features,
% VIS
and compare results to a block-design visual localizer.
% no refs in abstract (probably)
%\citep{sengupata2016extension}.  results: group AV
On a group level, a movie stimulus is associated with
increased activation spatially overlapping with a traditionally
localized PPA.
% results: group AD
In contrast, activation for an auditory stimulus is more restricted
to the anterior PPA.
% results: individual AD
On an individual level, hemodynamic responses
form bilateral clusters in the PPA of nine individuals and unilateral
clusters in another two.
% conclusion: generalizability
Results suggest that activation in the PPA generalizes beyond
pictures of landscapes to spatial information embedded in
a naturalistic movie and even an auditory narrative, and may
% conclusion: PPA has subregions
call for considering a functional subdivision of the PPA.
\end{abstract}
